opXRD: Open Experimental Powder X-ray Diffraction Database

### 2025-04-24 SI.tex
Pre-review changes commit

\affil[]{}
\author[ ]{Daniel Hollarek}
\author[ ]{Henrik Schopmans}
\author[ ]{Jona Östreicher}
\author[ ]{Jonas Teufel}
\author[ ]{Bin Cao}
\author[ ]{Adie Alwen}
\author[ ]{Simon Schweidler}
\author[ ]{Mriganka Singh}
\author[ ]{Tim Kodalle}
\author[ ]{Hanlin Hu}
\author[ ]{Gregoire Heymans}
\author[ ]{Maged Abdelsamie}
\author[ ]{Alexander Wieczorek}
\author[ ]{Siarhei Zhuk}
\author[ ]{Arthur Hardiagon}
\author[ ]{Ruth Schwaiger}
\author[ ]{François-Xavier Coudert}
\author[ ]{Moritz Wolf}
\author[ ]{Sebastian Siol}
\author[ ]{Carolin M. Sutter-Fella}
\author[ ]{Ben Breitung}
\author[ ]{Andrea M. Hodge}
\author[ ]{Tong-yi Zhang}
\author[ ]{Pascal Friederich}

@@

\section{Description of opXRD files on Zenodo}
The database comes in two zip archives, ``opxrd.zip'' and ``opxrd\_in\_situ.zip''. The latter contains the in-situ data with highly correlated patterns recorded through time series measurements. Within the .zip archives patterns are saved as .json files grouped in folders indicating the contributing institution. If an institution contributed data from several projects, the contributed data is further divided into folders indicating the research project. These research project folders are labeled alphabetically in the order they are introduced in section $3$. 
Each .json file contains a pattern recorded from an X-ray diffraction experiment. If available, the composition and structure of the investigated sample and experiment conditions are also included in this file. Patterns belonging to time series measurements are labeled with filenames that indicate the measurement series they belong to as well as their order in that series.

@@

\section{Combined pattern plots}
Figure~$\eqref{fig:combined}$ belowshows 50 randomly selected samples of the X-ray diffraction patterns found in each of the research projects contributed to the opXRD database.

>>>>

\author[ ]{Daniel Hollarek}
\author[ ]{Henrik Schopmans}
\author[ ]{Jona Östreicher}
\author[ ]{Jonas Teufel}
\author[ ]{Bin Cao}
\author[ ]{Adie Alwen}
\author[ ]{Simon Schweidler}
\author[ ]{Mriganka Singh}
\author[ ]{Tim Kodalle}
\author[ ]{Hanlin Hu}
\author[ ]{Gregoire Heymans}
\author[ ]{Maged Abdelsamie}
\author[ ]{Alexander Wieczorek}
\author[ ]{Siarhei Zhuk}
\author[ ]{Arthur Hardiagon}
\author[ ]{Ruth Schwaiger}
\author[ ]{François-Xavier Coudert}
\author[ ]{Moritz Wolf}
\author[ ]{Sebastian Siol}
\author[ ]{Carolin M. Sutter-Fella}
\author[ ]{Ben Breitung}
\author[ ]{Andrea M. Hodge}
\author[ ]{Tong-yi Zhang}
\author[*]{Pascal Friederich}

\affil[*]{Corresponding author: pascal.friederich@kit.edu}

@@

\section{Description of opXRD files on Zenodo}
The database comes in two zip archives, ``opxrd.zip'' and ``opxrd\_in\_situ.zip''. The latter contains the in-situ data with highly correlated patterns recorded through time series measurements. Within the .zip archives patterns are saved as .json files grouped in folders indicating the contributing institution. If an institution contributed data from several projects, the contributed data is further divided into folders indicating the research project. These research project folders are labeled alphabetically in the order they are introduced in Section~$3$. 
Each .json file contains a pattern recorded from an X-ray diffraction experiment. If available, the composition and structure of the investigated sample and experiment conditions are also included in this file. Patterns belonging to time series measurements are labeled with filenames that indicate the measurement series they belong to and their order in that series.

@@

\section{Combined pattern plots}
Figure~$\eqref{fig:combined}$ shows 50 randomly selected samples of the X-ray diffraction patterns found in each of the research projects contributed to the opXRD database.

### 2025-04-24 chapters/01_introduction.tex
Pre-review changes commit

% Simulated pattern machine learning successes + Sim/Exp performance gap
Machine learning has the potential to speed up the manual analysis of powder diffractograms and keep pace with an automated high-throughput experimentation environment\cite{Agrawal2019, Surdu2023}.
Models can be either trained to predict crystal structure information directly given a diffractogram, or they can be used to automate the conventional refinement workflow. In the latter case a model would first predict an initial crystal structure \cite{Surdu2023} which is then refined by a second model trained to perform the refinement process \cite{Feng2019}. So far due to an absence of labeled datasets with experimental diffractograms\cite{Wang2020}, machine learning in this domain has largely relied on diffractograms simulated from known structures\cite{Park2017, Lee2023} or, most recently, from generated synthetic crystals\cite{Schopmans2023}. 
Models trained on datasets with simulated diffractograms have already shown strong performance in predicting lattice parameters\cite{Dong2021, Chitturi2021, Habershon2004, zhang2024crystallographic}, spacegroup \cite{cao2024simxrd, Schopmans2023, Oviedo2018, Park2017, Vecsei2018, Zaloga2020, Suzuki2020, Chakraborty2021,zhang2024crystallographic}, and crystallite size \cite{Dong2021, Chakraborty2021} from simulated diffractograms.
However, the performance substantially drops off when these models are applied to data originating from experiments \cite{cao2024simxrd, Schopmans2023,zhang2024crystallographic, Wang2020, Vecsei2018}. This discrepancy in performance arises due to imperfections in experimental data which are not present in diffraction patterns modeled under ideal conditions. This is discussed in more detail below.

>>>>

% Simulated pattern machine learning successes + Sim/Exp performance gap
Machine learning has the potential to speed up the manual analysis of powder diffractograms and keep pace with an automated high-throughput experimentation environment\cite{Agrawal2019, Surdu2023}.
Models can be either trained to predict crystal structure information directly given a diffractogram, or they can be used to automate the conventional refinement workflow. In the latter case a model would first predict an initial crystal structure \cite{Surdu2023} which is then refined by a second model trained to perform the refinement process \cite{Feng2019}. So far due to an absence of labeled datasets with experimental diffractograms\cite{Wang2020}, machine learning in this domain has largely relied on diffractograms simulated from known structures\cite{Park2017, Lee2023} or, most recently, from generated synthetic crystals\cite{Schopmans2023}. 
Models trained on datasets with simulated diffractograms have already shown strong performance in predicting phases \cite{Park2017,chenAutomatingCrystalstructurePhase2021, changProbabilisticPhaseLabeling2023}, lattice parameters\cite{Dong2021, Chitturi2021, Habershon2004, zhang2024crystallographic}, spacegroup \cite{cao2024simxrd, Schopmans2023, Oviedo2018, Park2017, Vecsei2018, Zaloga2020, Suzuki2020, Chakraborty2021,zhang2024crystallographic}, and crystallite size \cite{Dong2021, Chakraborty2021} from simulated diffractograms.
However, the performance substantially drops off when these models are applied to data originating from experiments \cite{cao2024simxrd, Schopmans2023,zhang2024crystallographic, Wang2020, Vecsei2018}. This discrepancy in performance arises due to imperfections in experimental data which are not present in diffraction patterns modeled under ideal conditions. This is discussed in more detail below.

### 2025-04-24 chapters/04_our_dataset.tex
Pre-review changes commit

The variance of the data was analyzed using principal component analysis (PCA). PCA can be applied to datasets $X \subset \mathbb{R}^N$ to reduce the number of components needed to describe points $p \in X$ up to some tolerance in lost accuracy. In the context of PCA, the cumulative explained variance ratio is a measure of how much of the variance in the dataset $X$ can be explained using a given number of components. For a rigorous definition of PCA and the explained variance ratio, we refer to the literature \cite{Jolliffe2016}. Here, PCA was performed on datasets of X-ray diffraction patterns. These datasets $X$ are subsets of $\mathbb{R}^{N}$ with $N=512$ since each pattern $p \in X$ was standardized to have 512 intensity values spread out evenly from $0\degree$ to $180\degree$ using zero padding and interpolation with cubic splines. Hence the maximal components that could be needed to describe a dataset of diffraction data in this context is $N=512$. However, the maximal number of components is even lower for datasets that contain less than 512 patterns. In this case, the maximal number of components is equal to the number of patterns in the dataset since each pattern can add at most one degree of freedom to the dataset $X \in \mathbb{R}^N$. Hence the maximum number of components $N_{\text{max}}$ of a pattern dataset $X$ is given as follows:
\begin{align}
    N_{\text{max}} = \min(N_{\text{values}}, N_{\text{patterns}}).
      \label{eq:nmax}
\end{align}
Here $N_{\text{values}} =512$ is the number of recorded intensity values per pattern and $N_{\text{patterns}}$ is the number of patterns in the dataset $X$. Fig~$\eqref{fig:components}$ below shows the cumulative explained variance ratio over the fraction of maximal No. components $N_{\text{max}}$ as defined above. In this figure, a faster convergence of the cumulative variance ratio towards one indicates that the patterns in this data are relatively similar. The degree of variation between the patterns is different for each contribution. For example, the CRNS and the HKUST contributions each are collections that encompass many research projects over a large period of time and thus exhibit a high degree of variability between individual patterns. In contrast, the contributions by USC and LBNL contain many very similar patterns. The patterns in the USC datasets are similar because the underlying samples are all variations of \ce{CuNi} and \ce{CuAl} alloys. The patterns submitted by LBNL are similar because they stem from in-situ recordings where several hundred or several thousand patterns were collected over time per sample while they were undergoing physical conversion processes.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.85\linewidth]{figures/component_fractions.png}
    \caption{Explained variance ratio over the fraction of the maximum number of components for each dataset contributed to the opXRD database. Here the maximal No. components refers to $N_{\text{max}}$ as defined in equation $\eqref{eq:nmax}$. Datasets contributed by the same institution are labeled alphabetically in the order in which they are described in the texts towards the end of this section.}
    \label{fig:components}
\end{figure}

Fig.~$\eqref{fig:histograms}$ provides an overview of the distributions of pattern and structure properties in the opXRD dataset. Nearly all patterns have an angular resolution smaller than $\Delta(2\theta) = 0.1 ^\circ$. Here the angular resolution is defined as the range of recorded angles divided by the number of recorded intensity values along that range. For most patterns, the lowest recorded angle is smaller than $30 ^\circ$ and the highest recorded angle is smaller than $120 ^\circ$. The start-to-end angle distribution reveals that all diffractograms start in a narrow window between $0\degree$ and approximately $50\degree$, while they end between $50\degree$ and $150\degree$, with the majority of patterns going from $0\degree$ to approximately $70\degree$. Unlike most ML approaches using synthetic data over the full angle range with fixed resolution, the opXRD dataset has a strongly varying angle range and resolution. Hence, working with this data requires additional pre-processing methods such as padding and interpolation, or more flexible ML models beyond standard CNNs.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.78\linewidth]{figures/hist.png}
    \caption{Histograms detailing the distribution of pattern and structure properties in the opXRD database: a) distribution of spacegroups present in labeled data; b) distribution of angular resolution in all data; c) distribution of smallest and largest recorded $2\theta$ values for all data.}
    \label{fig:histograms}
\end{figure}

>>>>

The variance of the data was analyzed using principal component analysis (PCA). PCA can be applied to datasets $X \subset \mathbb{R}^N$ to reduce the number of components needed to describe points $p \in X$ up to some tolerance in lost accuracy. In the context of PCA, the cumulative explained variance ratio is a measure of how much of the variance in the dataset $X$ can be explained using a given number of components. For a rigorous definition of PCA and the explained variance ratio, we refer to the literature \cite{Jolliffe2016}. Here, PCA was performed on datasets of X-ray diffraction patterns. These datasets $X$ are subsets of $\mathbb{R}^{N}$ with $N=512$ since each pattern $p \in X$ was standardized to have 512 intensity values spread out evenly from $0\degree$ to $180\degree$ using zero padding and interpolation with cubic splines. Hence the maximal components that could be needed to describe a dataset of diffraction data in this context is $N=512$. However, the maximal number of components is even lower for datasets that contain less than 512 patterns. In this case, the maximal number of components is equal to the number of patterns in the dataset since each pattern can add at most one degree of freedom to the dataset $X \in \mathbb{R}^N$. Hence the maximum number of components $N_{\text{max}}$ of a pattern dataset $X$ is given as follows:
\begin{align}
    N_{\text{max}} = \min(N_{\text{values}}, N_{\text{patterns}}).
      \label{eq:nmax}
\end{align}
Here $N_{\text{values}} =512$ is the number of recorded intensity values per pattern and $N_{\text{patterns}}$ is the number of patterns in the dataset $X$. Fig~$\eqref{fig:components}$ below shows the cumulative explained variance ratio over the fraction of maximal No. components $N_{\text{max}}$ as defined above. In this figure, a faster convergence of the cumulative variance ratio towards one indicates that the patterns in this data are relatively similar. The degree of variation between the patterns is different for each contribution. For example, the CRNS and the HKUST contributions each are collections that encompass many research projects over a large period of time and thus exhibit a high degree of variability between individual patterns. In contrast, the contributions by USC and LBNL contain many very similar patterns. The patterns in the USC dataset are similar because the underlying samples are all variations of \ce{CuNi} and \ce{CuAl} alloys. The patterns submitted by LBNL are similar because they stem from in-situ recordings where several hundred or several thousand patterns were collected over time per sample while they were undergoing physical conversion processes.

\begin{figure}[!htb]
    \centering\includegraphics[width=0.85\linewidth]{figures/component_fractions.png}
    \caption{Explained variance ratio over the fraction of the maximum number of components for each dataset contributed to the opXRD database. Here the maximal No. components refers to $N_{\text{max}}$ as defined in equation $\eqref{eq:nmax}$. Datasets contributed by the same institution are labeled alphabetically in the order in which they are described in the texts towards the end of this section.}
    \label{fig:components}
\end{figure}

Fig.~$\eqref{fig:histograms}$ provides an overview of the distributions of pattern and structure properties in the opXRD database. Nearly all patterns have an angular resolution smaller than $\Delta(2\theta) = 0.1 ^\circ$. Here the angular resolution is defined as the range of recorded angles divided by the number of recorded intensity values along that range. For most patterns, the lowest recorded angle is smaller than $30 ^\circ$ and the highest recorded angle is smaller than $120 ^\circ$. The start-to-end angle distribution reveals that all diffractograms start in a narrow window between $0\degree$ and approximately $50\degree$, while they end between $50\degree$ and $150\degree$, with the majority of patterns going from $0\degree$ to approximately $70\degree$. Unlike most ML approaches using synthetic data over the full angle range with fixed resolution, the opXRD dataset has a strongly varying angle range and resolution. Hence, working with this data requires additional pre-processing methods such as padding and interpolation, or more flexible ML models beyond standard CNNs.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\linewidth]{figures/hist.png}
    \caption{Histograms detailing the distribution of pattern and structure properties in the opXRD database: a) distribution of spacegroups present in labeled data; b) distribution of angular resolution in all data; c) distribution of smallest and largest recorded $2\theta$ values for all data.}
    \label{fig:histograms}
\end{figure}

### 2025-04-24 chapters/06_summary_and_outlook.tex
Pre-review changes commit

With the opXRD dataset, a curation of $\numpatterns$ unlabeled and 2179 at least partially labeled experimental powder X-ray diffraction patterns from a wide range of different materials systems, we provide the largest currently available source of experimental XRD patterns. With this, we address the need for experimental data that arises when developing algorithms and analysis tools for pXRD data, both based on machine learning and classical approaches. The data can be used for the actual method development and for testing. Our dataset is a valuable and so far missing resource to drive further developments in the automated analysis of XRD data.

% How to contribute
Rather than a finished project, the opXRD dataset is an ongoing effort to collect experimental powder XRD data. We invite everyone who is working in the area of experimental powder XRD to submit it to the dataset, in order to further improve the utility of the dataset and thus aid further developments in this field. Our submission page (\url{https://xrd.aimat.science/}) and submission helper software will be kept available to collect more data. We will keep updating and maintaining the dataset with new incoming submissions.

>>>>

With the opXRD database, a curation of $\numpatterns$ unlabeled and 2179 at least partially labeled experimental powder X-ray diffraction patterns from a wide range of different materials systems, we provide the largest currently available source of experimental XRD patterns. With this, we address the need for experimental data that arises when developing algorithms and analysis tools for pXRD data, both based on machine learning and classical approaches. The data can be used for the actual method development and for testing. Our dataset is a valuable and so far missing resource to drive further developments in the automated analysis of XRD data.

% How to contribute
Rather than a finished project, the opXRD database is an ongoing effort to collect experimental powder XRD data. We invite everyone who is working in the area of experimental powder XRD to submit it to the dataset, in order to further improve the utility of the dataset and thus aid further developments in this field. Our submission page (\url{https://xrd.aimat.science/}) and submission helper software will be kept available to collect more data. We will keep updating and maintaining the dataset with new incoming submissions.

### 2025-04-24 main.tex
Pre-review changes commit

\author[\ITI,\INT]{Daniel Hollarek}
\author[\ITI,\INT]{Henrik Schopmans}
\author[\ITI,\INT]{Jona Östreicher}
\author[\ITI,\INT]{Jonas Teufel}
\author[\HKUSTGZ]{Bin Cao}
\author[\USC]{Adie Alwen}
\author[\INT]{Simon Schweidler}
\author[\LBLMF]{Mriganka Singh}
\author[\LBLMF,\LBLALS]{Tim Kodalle}
\author[\Hoffmann]{Hanlin Hu}
\author[\LBLCS]{Gregoire Heymans}
\author[\KFUPMMSE,\KFUPMIRCIMR]{Maged Abdelsamie}
\author[\CPT]{Arthur Hardiagon}
\author[\EMPA]{Alexander Wieczorek}
\author[\EMPA]{Siarhei Zhuk}
\author[\FZJIEMD]{Ruth Schwaiger}
\author[\EMPA]{Sebastian Siol}
\author[\CPT]{François-Xavier Coudert}
\author[\KITICRT]{Moritz Wolf}
\author[\LBLMF]{Carolin M. Sutter-Fella}
\author[\INT]{Ben Breitung}
\author[\USC]{Andrea M. Hodge}
\author[\HKUSTGZ]{Tong-yi Zhang}
\author[\ITI,\INT]{Pascal Friederich$^\ast$}

\affil[\ITI]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology (KIT), 76131 Karlsruhe, Germany.  E-mail: pascal.friederich@kit.edu} % Informatik-Hauptgebäude, Am Fasanengarten 5, 76131 Karlsruhe
\affil[\INT]{Institute of Nanotechnology, Karlsruhe Institute of Technology (KIT), 76131 Karlsruhe, Germany} % Hermann-von-Helmholtz-Platz 1
\affil[\HKUSTGZ]{Guangzhou Municipal Key Laboratory of Materials Informatics, Advanced Materials Thrust, Hong Kong University of Science and Technology (Guangzhou) (HKUST), Guangzhou 511400, China} % 1 Du Xue Road,
\affil[\USC]{Department of Chemical Engineering and Materials Science, University of Southern California (USC), Los Angeles CA 90089, USA} % 925 Bloom Walk
\affil[\LBLMF]{Molecular Foundry Division, Lawrence Berkeley National Laboratory (LBNL), Berkeley 94720 CA, USA}  %67 Cyclotron Rd, Berkeley, CA 94720, United States
\affil[\LBLALS]{Advanced Light Source, Lawrence Berkeley National Laboratory,  Berkeley 94720 CA, USA}  % 6 Cyclotron Rd, Berkeley, CA 94720, United States
\affil[\Hoffmann]{Hoffmann Institute of Advanced Materials, Shenzhen Polytechnic, Shenzhen 518055, China} % Liuxian Street NO.7098, Shenzhen 518055, China
\affil[\LBLCS]{Lawrence Berkeley National Laboratory (LBNL), Chemical Sciences Division, Berkeley 94720 CA, USA}  % 1 Cyclotron Rd, Berkeley, CA 94720, United States
\affil[\EMPA]{Empa–Swiss Federal Laboratories for Materials Science and Technology (EMPA), 8600 Dübendorf, Switzerland}  % Ueberlandstrasse 129, 8600 Dübendorf, Switzerland
\affil[\KITICRT]{Engler-Bunte-Institut \& Institute of Catalysis Research and Technology, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany}  %Hermann-von-Helmholtz-Platz 1
\affil[\CPT]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France} % 11 Rue Pierre et Marie Curie, 75005 Paris, France
\affil[\KFUPMMSE]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia} % 846R+8C2, Academic Belt Rd, KFUPM, Dhahran 34463, Saudi Arabia
\affil[\KFUPMIRCIMR]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia} %Academic Belt Road, Dhahran 31261, Saudi Arabia
\affil[\FZJIEMD]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany} %Wilhelm-Johnen-Straße, 52428 Jülich

\begin{document}

\maketitle

\begin{abstract}
\input{chapters/00_abstract}
\end{abstract}

@@

\subsection*{Acknowledgements}
We acknowledge financial support by the German Research Foundation (DFG) through the Research Training Group 2450 “Tailored Scale-Bridging Approaches to Computational Nanoscience”. We acknowledge support by the Federal Ministry of Education and Research (BMBF) under Grant No. 01DM21001B (German-Canadian Materials Acceleration Center). We acknowledge financial support from the Helmholtz Foundation Model Initiative within Project "SOL-AI". Part of this work was funded under the France 2030 framework by Agence Nationale de la Recherche (project ANR-22-PEXD-0009 of PEPR DIADEM). Work at the Molecular Foundry was supported by the Office of Science, Office of Basic Energy Sciences, of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231. Work at the Advanced Light Source (ALS) was done at beamline 12.3.2. The ALS is a DOE Office of Science User Facility under contract no. DE-AC02-05CH11231. The development of the online phase identification platform is supported by the Guangzhou-HKUST(GZ) Joint Funding Program (No. 2023A03J0003). Work by the USC group was supported by the National Science Foundation (NSF) grant numbers DMR-2227178 and OISE-2106597. Funding by the Helmholtz Research Program “Materials and Technologies for the Energy Transition (MTET), Topic 3: Chemical Energy Carriers" is kindly acknowledged. Work by the Empa group was supported by the Strategic Focus Area–Advanced Manufacturing (SFA–AM) through the project Advancing manufacturability of hybrid organic–inorganic semiconductors for large area optoelectronics (AMYS) as well as the Empa internal research call 2020.

>>>>

\author[\ITI,\INT]{Daniel Hollarek}
\author[\ITI,\INT]{Henrik Schopmans}
\author[\ITI,\INT]{Jona Östreicher}
\author[\ITI,\INT]{Jonas Teufel}
\author[\HKUSTGZ]{Bin Cao}
\author[\USC]{Adie Alwen}
\author[\INT]{Simon Schweidler}
\author[\LBLMF]{Mriganka Singh}
\author[\LBLMF,\LBLALS]{Tim Kodalle}
\author[\Hoffmann]{Hanlin Hu}
\author[\LBLCS]{Gregoire Heymans}
\author[\KFUPMMSE,\KFUPMIRCIMR]{Maged Abdelsamie}
\author[\CPT]{Arthur Hardiagon}
\author[\EMPA]{Alexander Wieczorek}
\author[\EMPA]{Siarhei Zhuk}
\author[\FZJIEMD]{Ruth Schwaiger}
\author[\EMPA]{Sebastian Siol}
\author[\CPT]{François-Xavier Coudert}
\author[\KITICRT]{Moritz Wolf}
\author[\LBLMF]{Carolin M. Sutter-Fella}
\author[\INT]{Ben Breitung}
\author[\USC]{Andrea M. Hodge}
\author[\HKUSTGZ]{Tong-yi Zhang}
\author[\ITI,\INT,*]{Pascal Friederich}

\affil[\ITI]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology (KIT), 76131 Karlsruhe, Germany.  E-mail: pascal.friederich@kit.edu} % Informatik-Hauptgebäude, Am Fasanengarten 5, 76131 Karlsruhe
\affil[\INT]{Institute of Nanotechnology, Karlsruhe Institute of Technology (KIT), 76131 Karlsruhe, Germany} % Hermann-von-Helmholtz-Platz 1
\affil[\HKUSTGZ]{Guangzhou Municipal Key Laboratory of Materials Informatics, Advanced Materials Thrust, Hong Kong University of Science and Technology (Guangzhou) (HKUST), Guangzhou 511400, China} % 1 Du Xue Road,
\affil[\USC]{Department of Chemical Engineering and Materials Science, University of Southern California (USC), Los Angeles CA 90089, USA} % 925 Bloom Walk
\affil[\LBLMF]{Molecular Foundry Division, Lawrence Berkeley National Laboratory (LBNL), Berkeley 94720 CA, USA}  %67 Cyclotron Rd, Berkeley, CA 94720, United States
\affil[\LBLALS]{Advanced Light Source, Lawrence Berkeley National Laboratory,  Berkeley 94720 CA, USA}  % 6 Cyclotron Rd, Berkeley, CA 94720, United States
\affil[\Hoffmann]{Hoffmann Institute of Advanced Materials, Shenzhen Polytechnic, Shenzhen 518055, China} % Liuxian Street NO.7098, Shenzhen 518055, China
\affil[\LBLCS]{Lawrence Berkeley National Laboratory (LBNL), Chemical Sciences Division, Berkeley 94720 CA, USA}  % 1 Cyclotron Rd, Berkeley, CA 94720, United States
\affil[\KFUPMMSE]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia} % 846R+8C2, Academic Belt Rd, KFUPM, Dhahran 34463, Saudi Arabia
\affil[\KFUPMIRCIMR]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia} %Academic Belt Road, Dhahran 31261, Saudi Arabia
\affil[\CPT]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France} % 11 Rue Pierre et Marie Curie, 75005 Paris, France
\affil[\EMPA]{Empa–Swiss Federal Laboratories for Materials Science and Technology (EMPA), 8600 Dübendorf, Switzerland}  % Ueberlandstrasse 129, 8600 Dübendorf, Switzerland
\affil[\FZJIEMD]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany} %Wilhelm-Johnen-Straße, 52428 Jülich
\affil[\KITICRT]{Engler-Bunte-Institut \& Institute of Catalysis Research and Technology, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany}  %Hermann-von-Helmholtz-Platz 1
\affil[*]{Corresponding author: pascal.friederich@kit.edu}

\begin{document}
\maketitle

\textbf{Keywords}: powder x-ray diffraction, machine learning, open-access data, crystal structure determination, phase identification
\begin{abstract}
\input{chapters/00_abstract}
\end{abstract}

@@

\subsection*{Acknowledgements}
H.S. acknowledges financial support by the German Research Foundation (DFG) through the Research Training Group 2450 “Tailored Scale-Bridging Approaches to Computational Nanoscience”. P.F. and D.H. acknowledge support by the Federal Ministry of Education and Research (BMBF) under Grant No. 01DM21001B (German-Canadian Materials Acceleration Center). J.Oe. and P.F. acknowledge financial support from the Helmholtz Foundation Model Initiative within Project "SOL-AI". Part of this work was funded under the France 2030 framework by Agence Nationale de la Recherche (project ANR-22-PEXD-0009 of PEPR DIADEM). Work at the Molecular Foundry was supported by the Office of Science, Office of Basic Energy Sciences, of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231. Work at the Advanced Light Source (ALS) was done at beamline 12.3.2. The ALS is a DOE Office of Science User Facility under contract no. DE-AC02-05CH11231. The development of the online phase identification platform is supported by the Guangzhou-HKUST(GZ) Joint Funding Program (No. 2023A03J0003). Work by the USC group was supported by the National Science Foundation (NSF) grant numbers DMR-2227178 and OISE-2106597. M.W. acknowledges funding by the Helmholtz Research Program “Materials and Technologies for the Energy Transition (MTET), Topic 3: Chemical Energy Carriers". Work by the Empa group was supported by the Strategic Focus Area–Advanced Manufacturing (SFA–AM) through the project Advancing manufacturability of hybrid organic–inorganic semiconductors for large area optoelectronics (AMYS) as well as the Empa internal research call 2020. We thank BWCloud, funded by the Ministry of Science, Research and Arts Baden-Württemberg, for providing cloud server infrastructure.

\clearpage

\begin{figure}
\centering
\textbf{Table of Contents}\\
\medskip
  \includegraphics{figures/TOC.png}
  \medskip
  \caption*{We introduce the Open Experimental Powder X-ray Diffraction Database (opXRD), the largest openly accessible collection of experimental powder diffractograms, comprising over 92,000 patterns collected across diverse material classes and experimental setups. Our ongoing effort aims to guide machine learning research toward fully automated analysis of pXRD data and to enable future self-driving materials labs.}
\end{figure}
